The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts

### 2020-05-21 write-up/covid-writeup.tex
Update covid-writeup.tex

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{setspace}
\DeclareGraphicsExtensions{.eps, .ps}
\usepackage{hyperref}
\usepackage{amsmath, amsthm, amsfonts}
% \usepackage[margin=1.5in]{geometry}

@@

\begin{document}
\title[The Hypothesis of Testing]{The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts} %

@@

Despite these steps, the data landscape for understanding COVID-19 remains limited.  Public databases maintained by \href{https://bit.ly/2UqFSuA}{Johns Hopkins University}~\citep{JHU_Lancet} and the \href{https://bit.ly/2vUHfrK}{New York Times}~\cite{NYT} provide incoming county-level information of confirmed cases and deaths.  Statisticians, epidemiologists, economists, and data scientists have used this granular data to forecast COVID-19 case-counts, deaths, and hospitalizations~\citep{Song2020,Ray2020,2020.IHME}.  In many cases, variations on the SIR models have been used to draw inferences about infection rates and intensity.  Parametric inference often uses observed case-count and/or observed COVID-19 related deaths to infer latent trajectories of the pandemic.

@@

Randomization of treatment assignment in clinical trials negates unobserved confounders.  This, however, does not negate effect modifiers.  Therefore, for marginal treatment effects to be interpretable, there must be a well-defined population.  Most often, our main interest is in causal effects on the population of COVID-19 positive.  Randomization within the clinical trial design yields internal validity, but we also need external validity to estimate the correct marginal effect of interest.

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{setspace}
\DeclareGraphicsExtensions{.eps, .ps}
\usepackage{amsmath, amsthm, amsfonts}
% \usepackage[margin=1.5in]{geometry}

@@

\begin{document}

\title[The Hypothesis of Testing]{The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts} %

@@

Despite these steps, the data landscape for understanding COVID-19 remains limited.  Public databases maintained by Johns Hopkins University~\citep{JHU_Lancet} and the New York Times~\cite{NYT} provide incoming county-level information of confirmed cases and deaths.  Statisticians, epidemiologists, economists, and data scientists have used this granular data to forecast COVID-19 case-counts, deaths, and hospitalizations~\citep{Song2020,Ray2020,2020.IHME}.  In many cases, variations on the SIR models have been used to draw inferences about infection rates and intensity.  Parametric inference often uses observed case-count and/or observed COVID-19 related deaths to infer latent trajectories of the pandemic.

@@

Randomization of treatment assignment in clinical trials negates unobserved confounders.  This, however, does not negate effect modifiers.  Therefore, for marginal treatment effects to be interpretable, there must be a well-defined population.  Most often, our main interest is in causal effects on the population of COVID-19 positive.  Randomization within the clinical trial design yields internal validity, but we also need external validity to estimate the correct marginal effect of interest~\cite{Keiding2016}.
